Strict Pure Functional Programming and Automatic Parallelization\\ (New-project-in-progess Paper)

### 2016-03-18 pubs/tfp16/paper.tex
TFP paper: Some more on testing, a bit on GC. WIP...

@@

We have developed a extensive test suite using the CMake \cite{cmake-book}
CTest tool. The full test suite is automatically run and any failures reported
using a Jenkins continuous integration server \cite{jenkins-book}. There are
test programs for both STG and mini-Haskell. We also run each test with various
levels of garbage collection enabled.

The test suite is partitioned into a number of directories which control what
testing is done for a specific program. Given our goal of exploring various
levels of strictness, most tests are run with all evaluation strategies (3
degrees of function strictness by two degrees of constructor strictness).
One interesting class of test programs are those which require non-strict
semantics. For these programs we test not only that the test leads to the expected
result with non-strict semantics, but also that the program returns a
"blackhole" in the case of strict semantics. Another important class of test
programs are those which should fail with a known error (e.g. a parsing error)
for these programs the test suite checks the output against an expected error
regular expression.

Extensive prelude.

Test suite of several hundred small programs.

Students learning Haskell and STG, writing Mini-Haskell and STG programs that
serendipitously go into our automated testing suite which is partitioned
according to our lattice of evaluation strategies (3 degrees of function
strictness by two degrees of constructor strictness), which tells us how much
non-strictness each program needs and something about the style in which
programs are written.

Continuous build system (Jenkins)

>>>>

We have implemented a simple copying garbage collector \cite{Cheney:1970}
with small "nurseries" in the multithreaded case \cite{Marlow:2008}. We have not
focused on the development of a moire sophisticated garbage collector, as the goal
of this project is to explore levels of strictness.

@@

We have developed a extensive test suite which uses the CMake \cite{cmake-book}
CTest tool. The full test suite is automatically run, and any failures reported,
after every comment to the version control system. We use a Jenkins continuous
integration server \cite{jenkins-book} to automate this build and testing process.
The (git) version control repository is hosted externally so our student
collaborators can contribute at their leisure.

There are several hundred small STG and mini-Haskell programs in the test suite.
It is partitioned into a number of directories which control what
testing is done for a specific program. Given our goal of exploring various
levels of strictness, most tests are run with all evaluation strategies (3
degrees of function strictness by two degrees of constructor strictness).
One interesting class of test programs are those which require non-strict
semantics. For these programs we test not only that the test leads to the expected
result with non-strict semantics, but also that the program returns a
"blackhole" in the case of strict semantics. Students who were Haskell/STG
beginners have contributed substantially to the test suite. We have also found
that the test suite has be of use as a learning tool for these students to
discover  what level of non-strictness was required for their programs,
a benefit that we did not initially envision. Over time we have developed
extensive STG and mini-haskell preludes of common programming patterns, to
aid in the writing of test programs.

Another important class of test programs are those which should fail with a
known error (e.g. a parsing error) for these programs the test suite checks
the output against an expected error regular expression. This class of test
programs has proved valuable in development and debugging of both the STG
and mini-haskell frontends.

We also run each test with various levels of garbage collection enabled, this
has helped us to find bugs not only in the garbage collector, but also in the
code generator.

debug level (runtime/compile time)
